---
title: "Consulting-Linguistic Project"
author: Shuyi Tan
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


# Setup 


```{r Load Package, message=FALSE}
library(dplyr)
library(readxl)
library(ggplot2)
library(scales)
library(tidyverse)
library(reshape2)
library(tidyr)
library(tidytext)
library(rstatix)
library(ggpubr)
```


```{r Load data}

#ENG_Les_diffe_rents_accents_du_franc_ais_August_25_2021 <- read_excel("Data/ENG - Les différents accents du français - August 25, 2021.xlsx")
raw_data <- ENG_Les_diffe_rents_accents_du_franc_ais_August_25_2021

#remove the first line
data <- raw_data[-1, ]

names(data)
```

```{r rename some columns}
data <- data %>%
  select(-c(Progress, `Duration (in seconds)`, Finished, RecordedDate, ResponseId, QID14, Q44, Q43...148, QID18_1, QID18_2, QID18_3, QID18_4,
            QID18_5, QID18_6, QID18_7, QID18_8, QID18_9, QID18_10, QID19)) %>%
  rename(gender = Q1,
         gender_other = Q1_4_TEXT, 
         age = Q2,
         country_of_birth = Q3,
         grow_up_province = Q41,
         grow_up_city = Q4,
         field_of_study = Q5,
         num_of_language = Q6,
         spoken_language = Q42, 
         spoken_language_other = Q42_11_TEXT,
         mother_tongue = Q7,
         mother_tongue_other = Q7_11_TEXT,
         year_of_french = Q8,
         french_speaking_place = Q9,
         french_speaking_place_other = Q9_6_TEXT,
         month_live_in_fr_env = Q43...22,
         type_of_french = Q10,
         type_of_french_other = Q10_3_TEXT,
         teacher_origin = Q11, 
         teacher_origin_other = Q11_3_TEXT
         ) %>% 
  mutate(age = as.numeric(age),
         num_of_language = as.numeric(num_of_language),
         year_of_french = as.numeric(year_of_french),
         )
  
#  check the data type of each column
#str(data) 
```



```{r convert character to factor}
data <- data %>%
  mutate_if(is.character, as.factor)
```

# Recording info

## Accent

1A: Quebec 
2A: France 
3A: Acadia 
4A: French Second Language 
5A: Africa 
6A: Quebec 
7A: Africa
8A: Acadia 
9A: France 
10A: French Second Language 


## Pictures 
White
White
White
White 
White?
Black
Black
Black
Asian 
Black
Black
White
Black 

## Summary 

White woman (brown sweater, brown hair) - 1A - Quebec 
White woman (brown T-shirt with flower) - 4A - English
White woman (black sweater, blonde hair) - 5A - Africa (ignore)
White woman (pink sweater) - 7A - Africa  (ignore)
Black woman (braided hair) - 2A France (ignore)
Black woman (no hair)- 6A - Quebec
Black woman (maroon T-shirt, glasses) - 9A France (ignore)
Black woman (bum hairstyle) - 3A - Acadia
Black woman (big circular earrings) - 10A - English 
White woman (gray sweater) - 8A - Acadia


---------------------------------------------------------------------------------
What we have now: 
1A - Quebec - White
4A - English - White
6A - Quebec - Black
3A - Acadia - Black
10A - English - Black
8A - Acadia - White


=================================================================================

Questionnaire:

1. To which gender to you identify?
- women
- men
- prefer not to answer
- prefer to define myself: ___________

2. How old are you?

3. In what country were you born? If it’s in Canada, in what province or territory?

4. In what city, town or village have you grown up? (More than one answer is possible.)

5. What is your field of studies? 

6. How many languages do you speak? Which ones?

7. What is your first language? Or what are your first languages?

8. For how many years have you been studying French?

9. Have you lived or spent time in Quebec, France, or in another French-speaking country? If so, for how many months?

10. What French accent would you prefer to learn?
- Quebec French
- France French
- other variety of French (specify): _______________

11. Your French teacher(s) are/were mainly of what origin?
- French
- Quebec
- other (specify): ___________________


# EDA (Descriptive data and visualization) 

There are 44 females and 12 males
```{r gender}

data %>% select(gender) %>% 
  group_by(gender) %>%
  tally() %>% 
  mutate(prop = percent(n/sum(n)))
```

One respondent did not disclose his/her age. The ages of participants range from 18 to 39, with the mean lying in 22. 
```{r age, warning=FALSE}
data$age <-  raw_data %>% select(Q2) %>% slice(2:n())
data$age <- as.numeric(unlist(data$age))

# summary data
data %>% select(age) %>%
  drop_na() %>%
  summarize(min = min(age),
            max = max(age),
            mean = mean(age))

# visualization
data %>% select(age) %>%
  drop_na() %>% 
  ggplot(aes(x = age)) + 
  geom_density() + 
  # add a vertical line for the average value 
  geom_vline(aes(xintercept=mean(age)),
            color="blue", linetype="dashed", size=1) + 
  labs(y = 'density') + 
  annotate(x= mean(data$age, na.rm = TRUE),y=+Inf,label="Mean = 21.6",vjust=2,geom="label")

```

 Out of 56 participants, almost half of them comes from Canada (27). For the rest, a majority of participants are from Asia, which is followed by America, Europe, and Africa. 
```{r country/area of birth, warning = FALSE}
# check how many participants come from Canada
data %>% select(country_of_birth) %>%
  mutate(country_general = ifelse(country_of_birth == 'Canada', 'Canada', 'Outside of Canada'))  %>% 
  group_by(country_general) %>%
  tally()


# visualize the proportions of participants who aren't from Canada by Continent 
as.data.frame(data %>% 
  select(country_of_birth) %>%
  filter(country_of_birth != 'Canada') %>%
  mutate(continent = case_when(country_of_birth %in% c('Pakistan', 'Philippines', 'China', 'Hong Kong (S.A.R.)', 'India', 'Iran', 'Japan', 'Kazakhstan', 'South Korea', 'Taiwan') ~ 'Asia',
                              country_of_birth %in% c('Brazil', 'Colombia', 'United States of America') ~ 'America',
                              country_of_birth %in% c('Croatia', 'Czech Republic', 'Russian Federation', 'United Kingdom of Great Britain and Northern Ireland') ~ 'Europe',
                              country_of_birth %in% c('Mauritius', 'Tunisia') ~ 'Africa')) %>%
  group_by(continent) %>% 
  tally()) %>%  
  ggplot(aes(x = continent, y = n, fill = continent)) + 
  geom_col() + 
  labs(y = 'count') + 
  geom_text(aes(label = n), vjust = -0.5)

```

Among 27 participants who was born in Canada, 18 of them grew up in BC. 
```{r province/territory}
data %>% 
  filter(country_of_birth == 'Canada') %>%
  select(grow_up_province) %>% 
  mutate(Grow_up_Province = ifelse(grow_up_province == "BC", 'Live in BC', 'Live outside BC')) %>%
  group_by(Grow_up_Province) %>%
  tally() 

```

Out of 56 participants, the fields of study of 13 people were/are French. One side note: 2 people have linguistics backgrounds. 
```{r Field of Study}
data %>% select(field_of_study) %>%
  mutate(french_major = ifelse(str_detect(field_of_study, "French"), TRUE, FALSE)) %>%
  group_by(french_major) %>% 
  tally()
```

Around half of participants speak three languages, which is followed by two languages, four languages, and over five languages. To be specific, all participants are at least English and French speakers
```{r Language They Speak}
language_df <- as.data.frame(data %>% 
  group_by(num_of_language) %>%
  tally())
  
language_df$num_of_language <- factor(language_df$num_of_language, levels = c("2", "3", "4", "+ de 5"))

language_df %>% 
  ggplot(aes(x= num_of_language, y= n, fill = num_of_language)) + 
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) + 
  xlab("How many languages do you speak?") 

nrow(data %>% 
  select(spoken_language) %>%
  filter(str_detect(spoken_language, 'French')))

nrow(data %>% 
  select(spoken_language) %>%
  filter(str_detect(spoken_language, 'English')))

```

```{r Mother Tongue}

language_df_II <- data %>% 
  select(mother_tongue) %>%
  mutate(English = ifelse(str_detect(mother_tongue, "English") | str_detect(mother_tongue, "Anglais"), TRUE, FALSE),
         Cantonese = ifelse(str_detect(mother_tongue,"Cantonese"), TRUE, FALSE),chabu 
         Hindi = ifelse(str_detect(mother_tongue,"Hindi"), TRUE, FALSE),
         Mandarin = ifelse(str_detect(mother_tongue,"Mandarin"), TRUE, FALSE),      
         Korean = ifelse(str_detect(mother_tongue,"Korean"), TRUE, FALSE),
         Persian = ifelse(str_detect(mother_tongue,"Persian"), TRUE, FALSE),      
         Spanish = ifelse(str_detect(mother_tongue,"Spanish"), TRUE, FALSE),    
         Tagalog = ifelse(str_detect(mother_tongue,"Tagalog"), TRUE, FALSE))   

language_count = matrix(NA, nrow = 6, ncol = 2)

language_count[,1] <- names(language_df_II)[2:7]

for (i in 1:6){
  language_count[i,2] = as.numeric(table(language_df_II[,i+1]))[2]
}
  
language_count <- as.data.frame(language_count)
colnames(language_count) = c('mother_tongue', 'n')

# Visualization
rbind(language_count, data %>%
  select(mother_tongue_other) %>%
  drop_na() %>%
  group_by(mother_tongue_other) %>%
  tally() %>%
  rename(mother_tongue = mother_tongue_other)) %>%
  mutate(n = as.numeric(n)) %>%
  arrange(desc(n)) %>% 
  ggplot(aes(x = reorder(mother_tongue, n), y = n)) +
  geom_col() + 
  geom_text(aes(label = n), hjust = -0.5) + 
  coord_flip() + 
  labs(x = 'Mother Tongue', y = 'Count') + 
  theme_minimal()
```

```{r Years of Studying French}

# pie chart 
year_of_studying_french_df %>% 
  tally() %>% 
  ggplot(aes(x="", y = n, fill=year_group))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y") + 
  scale_fill_discrete(name = "Years of Studying French") 
  
# barchart
  
year_of_studying_french_df %>% 
  tally() %>% 
  ggplot(aes(x = year_group, y =n, fill=year_group)) +
  geom_col()+
  geom_text(aes(label = n), vjust = -0.5) + 
  labs(x = 'Years of Studying French', y = 'count')
```
10. What French accent would you prefer to learn?
- Quebec French
- France French
- other variety of French (specify): 


The number/proportion of preference for European French is over three times of that of Quebec! 
```{r Preferred French to Learn}
data %>% 
  select(type_of_french) %>% 
  mutate(type_of_french=replace(type_of_french, type_of_french== 'Français de France', 'French from France')) %>%
  group_by(type_of_french) %>%
  tally() %>% 
  slice_head(n = 3) %>%
  add_row(type_of_french = "Belgium, Franco-Ontario or Cajun", n = 2) %>%
  #mutate(type_of_french = replace(type_of_french, type_of_french == "Other variety of French (specify)", "Belgium, Franco-Ontario or Cajun")) %>%
  mutate(per =`n`/sum(`n`),
         label = paste0(n, ' (', scales::percent(per), ')')) %>% 
  ggplot(aes(x="", y = per, fill = type_of_french))+
  geom_bar(stat="identity", width = 1) +
  coord_polar("y", start=0, direction = - 1)+
  theme_void()+
  geom_text(aes(x=0.9, y = cumsum(per) - per/2, label= label)) + 
  scale_fill_discrete(name = "Preferred French to Learn") 
```


9. Have you lived or spent time in Quebec, France, or in another French-speaking country? 

Out of 56 people, 48.2%	of participants lived in Quebec, 42.9% o f participants lived in France, 1.8% (1) of participants lived in other French-speaking areas, 28.6% of participants have never lived in any French-speaking areas. 


```{r Lived/Spent time in French-speaking area}

data %>% 
  select(french_speaking_place) %>% 
  drop_na()

# translate into English
live_in_french_env_df <- data %>% select(french_speaking_place) %>% 
  mutate(french_speaking_place_eng = case_when(french_speaking_place == "en France?"~'France',
                                               french_speaking_place =="au Québec?,en France?"~'Québec, France',
                                               french_speaking_place =="au Québec?"~'Québec',
                                               french_speaking_place =="ailleurs dans le monde francophone? Si oui, précisez où:"~'Other',
                                               french_speaking_place =="en France?,ailleurs dans le monde francophone? Si oui, précisez où:"~'France, Other',
                                               french_speaking_place =="au Québec?,en France?,ailleurs dans le monde francophone? Si oui, précisez où:" ~ 'Québec, France, Other',
                                               french_speaking_place == NA~'Never')) 


as.data.frame(t(live_in_french_env_df %>% 
  group_by(french_speaking_place_eng) %>% 
  tally() %>%
  mutate(live_in_France = ifelse(str_detect(french_speaking_place_eng, 'France'), n, NA),
         live_in_quebec = ifelse(str_detect(french_speaking_place_eng, 'Québec'), n, NA),
         none = ifelse(is.na(french_speaking_place_eng), n, NA),
         other = ifelse(french_speaking_place_eng == 'Other', n, NA),
         ) %>%
  summarize(France_count = sum(live_in_France, na.rm = TRUE),
               Quebec_count = sum(live_in_quebec, na.rm = TRUE),
               none_count = sum(none, na.rm = TRUE),
               other_count = sum(other, na.rm = TRUE)) %>%
  # I found two people two choose "other" wrote "non" in the open-ended question
  mutate(none_count = none_count + 2,
         other_count = other_count -2 ))) %>%
  rename(Count = V1) %>% 
  mutate(Area = c('France', 'Quebec', 'None', 'Other'),
         Prop = percent(Count/nrow(data))) %>% 
  arrange(desc(Count))
```



10 continued: if so, for how many months?

```{r months of living in French-speaking area}
#unique(data$month_live_in_fr_env)

month_live_in_fr_env_df <- data %>% 
  select(month_live_in_fr_env) %>%
  drop_na() %>%
  mutate(month_live_in_fr_env_eng = case_when(month_live_in_fr_env == 'Moins de 1 mois'~'<1',
                                              month_live_in_fr_env == 'Entre 4 et 6 mois'~'4-6',
                                              month_live_in_fr_env == 'Entre 1 et 3 mois' ~'1-3',
                                              month_live_in_fr_env == 'Plus de 12 mois'~'>12',
                                              month_live_in_fr_env == 'Entre 7 et 12 mois'~'7-12')) %>%
  group_by(month_live_in_fr_env_eng) %>% 
  tally()


month_live_in_fr_env_df$month_live_in_fr_env_eng <- factor(month_live_in_fr_env_df$month_live_in_fr_env_eng,
                                                           levels = c("<1", "1-3", "4-6", "7-12", ">12"))

month_live_in_fr_env_df %>% ggplot(aes(x = month_live_in_fr_env_eng, y = n)) + 
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) + 
  #coord_flip() + 
  labs(x = 'Months of Living in French-speaking Places', y = 'Month') + 
  theme_minimal()
```



```{r Teacher Origin}

teacher_origin_df <- data %>% 
  select(teacher_origin) %>% 
  mutate(teacher_origin_eng = case_when(teacher_origin == "French"~"France",
                                        teacher_origin == "Québécoise"~'Québec',
                                        teacher_origin == "Autre(s) (précisez)" ~ 'Other')) %>% 
  group_by(teacher_origin_eng) %>% 
  tally() %>%
  rename(teacher_origin = teacher_origin_eng)


teacher_original_other_df <- data %>% 
  select(teacher_origin_other) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "From everywhere, I had teachers from France, Quebec, and French Second Languages (FSL)", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "mélange + Franco-Ontarian + Haiti + many regions in Africa (Egypte/Sénégal/Côte d'Ivoire...etc)", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "French, Tanzanian, Mauritian", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Both French and Quebec.", "Both France and Québec")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Both French and Quebecois", "Both France and Québec")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "I think 3 teachers from Quebec and 2 from France.","Both France and Québec")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Both French and Quebecois, and also Anglophones", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Franco-Ontarian", "Franco-ontarian")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "I don't know", NA)) %>% 
  group_by(teacher_origin_other) %>%
  tally() %>% 
  rename(teacher_origin = teacher_origin_other)


rbind(teacher_origin_df, teacher_original_other_df %>% slice_head( n = 3)) %>% 
  slice(1: 6) %>%
  mutate(n = replace(n, n == 11, 12)) %>% 
  ggplot(aes(x = reorder(teacher_origin, n), y = n)) + 
  geom_col() + 
  coord_flip() + 
  geom_text(aes(label = n), hjust = -0.5) + 
  labs(x = 'Original of French Teacher', y = 'Count')
```


```{r preferred French to learn vs. Teacher Origin}
chisq.test(data$type_of_french, data$teacher_origin)
fisher.test(data$type_of_french, data$teacher_origin)
```

# Statistical Tests

Question: speaking the same french accent, will white speakers receive more positive feedback? 

* Feeling of Perception 

1) I think this is beautiful French.
--------------------------------------

* Understandability

2) Is it rather easy or difficult to understand the speaker?
3) Would the person who did the recording be a good French teacher at UBC?
4) The speaker’s accent is weak, strong, or absent?
--------------------------------------
* Solidarity dimension
5) This person is dynamic.
6) This person is nice.
7) This person is social.
--------------------------------------
* Status traits
8) This person is professional.
9) This person is leader.
10) This person is educated.


Recall: 
1A - Quebec - White
4A - English - White
6A - Quebec - Black
3A - Acadia - Black
10A - English - Black
8A - Acadia - White

Scales :

1 = I strongly disagree
2 = I disagree
3  = I slightly disagree
4  = I slightly agree
5 = I agree
6 = I strongly agree


```{r pick certain columns}
positions <- c(21:30, 43:52, 54:63, 76:85, 98:107, 120:129)
# data of 1A, 3A, 4A, 6A, 8A, and 10A
recording_temp <- data %>% select(positions) 
recording_temp <- as.data.frame(sapply(recording_temp, as.numeric))

names(recording_temp)
```

1A - Quebec - White
4A - English - White
6A - Quebec - Black
3A - Acadia - Black
10A - English - Black
8A - Acadia - White

```{r impute the recording df}
# I have to rename these columns because the mice package cannot recognize the original columns names
names(recording_temp) <- c("quebec_w_1","quebec_w_2","quebec_w_3","quebec_w_4","quebec_w_5","quebec_w_6","quebec_w_7","quebec_w_8","quebec_w_9","quebec_w_10" , # 1A - Quebec - White
                           "aca_b_1","aca_b_2","aca_b_3","aca_b_4","aca_b_5","aca_b_6","aca_b_7","aca_b_8","aca_b_9","aca_b_10", # 3A - Acadia - Black
                           "eng_w_1","eng_w_2","eng_w_3","eng_w_4","eng_w_5","eng_w_6","eng_w_7","eng_w_8","eng_w_9","eng_w_10", # 4A - English - White
                           "quebec_b_1","quebec_b_2","quebec_b_3","quebec_b_4","quebec_b_5","quebec_b_6","quebec_b_7","quebec_b_8","quebec_b_9","quebec_b_10", # 6A - Quebec - Black
                           "aca_w_1","aca_w_2","aca_w_3","aca_w_4","aca_w_5","aca_w_6","aca_w_7","aca_w_8","aca_w_9","aca_w_10" , # 8A - Acadia - White
                           "eng_b_1" ,"eng_b_2", "eng_b_3" ,"eng_b_4" ,"eng_b_5",  "eng_b_6" , "eng_b_7",  "eng_b_8" , "eng_b_9","eng_b_10") # 10A - English - Black

# impute the data because we are suffering from severe data missingness
record_imp <- mice::mice(recording_temp,m=5,maxit=50,meth='pmm',seed=500)
rec_imputed <- mice::complete(record_imp,1)

```


## beautiful french 

```{r beautiful french - anova}
beau_fren <- rec_imputed %>% 
  select(quebec_w_1, quebec_b_1, eng_w_1, eng_b_1, aca_b_1, aca_w_1) %>%
  mutate(english_accent = rowSums(.[3:4]),
         quebec_accent = rowSums(.[1:2]),
         acadian_accent = rowSums(.[5:6])) %>%
  select(english_accent, quebec_accent, acadian_accent) %>%
  mutate(id = 1:nrow(rec_imputed))


# convert to long format 
beau_fren_long <- beau_fren %>%
  gather(key = "accent", value = "value", english_accent, quebec_accent, acadian_accent) %>%
  convert_as_factor(id, accent)


# summary stat
beau_fren_long %>% 
  group_by(accent) %>%
  get_summary_stats(value, type = "mean_sd")

# repeated measures ANOVA
# warning: the normality assumption doesn't satisfy, but it's super sensitive to sample size
res_beau_fr<- get_anova_table(anova_test(data = beau_fren_long, dv = value, wid = id, within = accent))

# pairwise paired t-tests

beau_fr_pw <- beau_fren_long %>%
  pairwise_t_test(
    value ~ accent, paired = TRUE,
    p.adjust.method = "bonferroni"
    ) %>%  mutate(y.position = c(13, 14.5, 16))

p_beautiful <- ggboxplot(beau_fren_long, x = "accent", y = "value", fill = "accent") + 
  rremove('legend') + 
  rremove('xlab') + 
  stat_pvalue_manual(beau_fr_pw, vjust = - 0.3, bracket.nudge.y = 0.5, label = "p = {p.adj}", size = 3) + 
  labs(
    subtitle = get_test_label(res_beau_fr, detailed = TRUE),
    caption = get_pwc_label(beau_fr_pw),
    title = 'Beautiful',
    y = 'Score',
  ) + 
  theme(plot.caption = element_text(size=10),
        plot.subtitle=element_text(size=10, vjust= 1, face="italic", color="black"),
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size=13, face = 'bold'))
  
```

1A - Quebec - White
4A - English - White
6A - Quebec - Black
3A - Acadia - Black
10A - English - Black
8A - Acadia - White

```{r}
names(rec_imputed)
```


```{r Solidarity dimension}
sd_french <- rec_imputed %>% 
   select("eng_w_5", "eng_b_5",
          "eng_w_6", "eng_b_6",
          "eng_w_7", 'eng_b_7',
          'quebec_w_5', 'quebec_b_5',
          'quebec_w_6', 'quebec_b_6',
          'quebec_w_7', 'quebec_b_7',
          'aca_w_5', 'aca_b_5',
          'aca_w_6', 'aca_b_6',
          'aca_w_7', 'aca_b_7') %>% 
   mutate(english_dynamic = rowSums(.[1:2]),
         english_nice = rowSums(.[3:4]),
         english_social = rowSums(.[5:6]),
         quebec_dynamic = rowSums(.[7:8]),
         quebec_nice = rowSums(.[9:10]),
         quebec_social = rowSums(.[11:12]), 
         acadian_dynamic = rowSums(.[13:14]),
         acadian_nice = rowSums(.[15:16]),
         acadian_social = rowSums(.[17:18])) 

dynamic_df <- sd_french %>% 
  select(english_dynamic, quebec_dynamic, acadian_dynamic) %>%
  rename(English = english_dynamic,
         Quebec = quebec_dynamic,
         Acadian = acadian_dynamic) %>% 
  mutate(id = 1: nrow(sd_french)) %>% 
    gather(key = "accent", value = "value", English, Quebec, Acadian) %>%
  convert_as_factor(id, accent)

nice_df <- sd_french %>% 
  select(english_nice, quebec_nice, acadian_nice) %>%
  rename(English = english_nice,
         Quebec = quebec_nice,
         Acadian = acadian_nice) %>% 
  mutate(id = 1: nrow(sd_french)) %>% 
    gather(key = "accent", value = "value", English, Quebec, Acadian) %>%
  convert_as_factor(id, accent)

social_df <- sd_french %>% 
  select(english_social, quebec_social, acadian_social) %>%
  rename(English = english_social,
         Quebec = quebec_social,
         Acadian = acadian_social) %>% 
  mutate(id = 1: nrow(sd_french)) %>% 
    gather(key = "accent", value = "value", English, Quebec, Acadian) %>%
  convert_as_factor(id, accent)

####################################################################################################################################
# Dynamic
dynamic_df %>% 
  group_by(accent) %>%
  get_summary_stats(value, type = "mean_sd")  

res_dynamic <- get_anova_table(anova_test(data = dynamic_df, dv = value, wid = id, within = accent))
  

dynamic_pw <- dynamic_df %>%
  pairwise_t_test(
    value ~ accent, paired = TRUE,
    p.adjust.method = "bonferroni"
    ) %>% 
  mutate(y.position = c(13, 14.5, 16)) 

p_dynamic <- ggboxplot(dynamic_df, x = 'accent', y = "value", fill = "accent") + 
  rremove('legend') + 
  rremove('xlab') + 
  stat_pvalue_manual(dynamic_pw, vjust = - 0.3, bracket.nudge.y = 0.5, label = "p = {p.adj}", size = 3) + 
  labs(
    subtitle = get_test_label(res_dynamic, detailed = TRUE),
    caption = get_pwc_label(dynamic_pw),
    y = 'Score',
    title = 'Dynamic'
  ) + 
  theme(plot.caption = element_text(size=10),
        plot.subtitle=element_text(size=10, vjust= 1, face="italic", color="black"),
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size=13, face = 'bold'))


####################################################################################################################################

# Nice

nice_df %>% 
  group_by(accent) %>%
  get_summary_stats(value, type = "mean_sd")  

res_nice <- get_anova_table(anova_test(data = nice_df, dv = value, wid = id, within = accent))
  

nice_pw <- nice_df %>%
  pairwise_t_test(
    value ~ accent, paired = TRUE,
    p.adjust.method = "bonferroni"
    ) %>% 
  mutate(y.position = c(13, 14.5, 16))

p_nice <- ggboxplot(nice_df, x = 'accent', y = "value", fill = "accent") + 
  rremove('legend') + 
  rremove('xlab') + 
  stat_pvalue_manual(nice_pw, vjust = - 0.3, bracket.nudge.y = 0.5, label = "p = {p.adj}", size = 3) + 
  labs(
    subtitle = get_test_label(res_nice, detailed = TRUE),
    caption = get_pwc_label(nice_pw),
    title = 'Nice',
    y = 'Score',
  ) + 
  theme(plot.caption = element_text(size=10),
        plot.subtitle=element_text(size=10, vjust= 1, face="italic", color="black"),
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size=13, face = 'bold'))

####################################################################################################################################


social_df %>% 
  group_by(accent) %>%
  get_summary_stats(value, type = "mean_sd")  

res_social <- get_anova_table(anova_test(data = social_df, dv = value, wid = id, within = accent))
  

social_pw <- social_df %>%
  pairwise_t_test(
    value ~ accent, paired = TRUE,
    p.adjust.method = "bonferroni"
    ) %>% 
  mutate(y.position = c(13, 14.5, 16))

p_social <- ggboxplot(social_df, x = 'accent', y = "value", fill = "accent") + 
  rremove('legend') + 
  rremove('xlab') + 
  stat_pvalue_manual(social_pw, vjust = - 0.3, bracket.nudge.y = 0.5, label = "p = {p.adj}", size = 3) + 
  labs(
    subtitle = get_test_label(res_social, detailed = TRUE),
    caption = get_pwc_label(social_pw),
    title = 'Social',
    y = 'Score',
  ) + 
  theme(plot.caption = element_text(size=10),
        plot.subtitle=element_text(size=10, vjust= 1, face="italic", color="black"),
        axis.text.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size=13, face = 'bold'))

```

```{r Solidarity dimension - viz, fig.height= 7.9, fig.width= 8}
# plot
cowplot::plot_grid(p_beautiful,p_dynamic, p_nice, p_social)

# table
res_tbl_ds <- matrix(NA, nrow = 3, ncol = 5)

res_tbl_ds[1, 1:3]  <- pull(dynamic_df %>% 
  group_by(accent) %>% 
  summarize(mean = round(mean(value), 1)), mean)

res_tbl_ds[2, 1:3]  <-pull(nice_df %>% 
  group_by(accent) %>% 
  summarize(mean = round(mean(value), 1)), mean)

res_tbl_ds[3, 1:3]  <- pull(social_df %>% 
  group_by(accent) %>% 
  summarize(mean = round(mean(value), 1)), mean)


res_tbl_ds[, 4] <- c(res_dynamic$F, res_nice$F, res_social$F)
res_tbl_ds[, 5] <- c(res_dynamic$p, res_nice$p, res_social$p)

res_tbl_ds <- as.data.frame(res_tbl_ds)
colnames(res_tbl_ds) <- c('mean_English', 'mean_Quebec', 'mean_acadia', 'F', 'p-value')
rownames(res_tbl_ds) <- c('Dynamic', 'Nice', 'Social')
res_tbl_ds
```



```{r beautiful french - LME, message=FALSE}
library(lme4)

summary(lmer(value ~ accent + (1|id), data = beau_fren_long))
```


```{r}
fit_lm = lmList(value ~ accent)
```









































