---
title: "Consulting-Linguistic Project"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---


# Setup 

```{r Download Package}
install.packages('dplyr')
install.packages('readxl')
install.packages('ggplot2')
install.packages('scales')
install.packages('tidyverse')
install.packages('reshape2')
install.packages('tidyr')
install.packages('tidytext')
```


```{r Load Package}
library(dplyr)
library(readxl)
library(ggplot2)
library(scales)
library(tidyverse)
library(reshape2)
library(tidyr)
library(tidytext)
```


```{r Load data}

ENG_Les_diffe_rents_accents_du_franc_ais_August_25_2021 <- read_excel("Data/ENG - Les différents accents du français - August 25, 2021.xlsx")
raw_data <- ENG_Les_diffe_rents_accents_du_franc_ais_August_25_2021

#remove the first line
data <- raw_data[-1, ]

names(data)
```

```{r rename some columns}
data <- data %>%
  select(-c(Progress, `Duration (in seconds)`, Finished, RecordedDate, ResponseId, QID14, Q44, Q43...148)) %>%
  rename(gender = Q1,
         gender_other = Q1_4_TEXT, 
         age = Q2,
         country_of_birth = Q3,
         grow_up_province = Q41,
         grow_up_city = Q4,
         field_of_study = Q5,
         num_of_language = Q6,
         spoken_language = Q42, 
         spoken_language_other = Q42_11_TEXT,
         mother_tongue = Q7,
         mother_tongue_other = Q7_11_TEXT,
         year_of_french = Q8,
         french_speaking_place = Q9,
         french_speaking_place_other = Q9_6_TEXT,
         month_live_in_fr_env = Q43...22,
         type_of_french = Q10,
         type_of_french_other = Q10_3_TEXT,
         teacher_origin = Q11, 
         teacher_origin_other = Q11_3_TEXT,
         Q18_beautiful_french = QID18_1,
         Q18_easy_to_understand = QID18_2,
         Q18_suitable_to_teach = QID18_3,
         Q18_strong_accent = QID18_4,
         Q18_dynamic = QID18_5,
         Q18_nice = QID18_6,
         Q18_sociable = QID18_7,
         Q18_professional = QID18_8,
         Q18_leadership = QID18_9,
         Q18_educated = QID18_10,
         Q19_speaker_from = QID19
         ) %>% 
  mutate(age = as.numeric(age),
         num_of_language = as.numeric(num_of_language),
         year_of_french = as.numeric(year_of_french),
         )
  
str(data) 
```




```{r convert character to factor}
data <- data %>%
  mutate_if(is.character, as.factor)
```

# Recording info

## Accent

1A: Quebec 
2A: France 
3A: Acadia 
4A: French Second Language 
5A: Africa 
6A: Quebec 
7A: Africa
8A: Acadia 
9A: France 
10A: French Second Language 


## Pictures 
White
White
White
White 
White?
Black
Black
Black
Asian 
Black
Black
White
Black 


=================================================================================

Questionnaire:

1. To which gender to you identify?
- women
- men
- prefer not to answer
- prefer to define myself: ___________

2. How old are you?

3. In what country were you born? If it’s in Canada, in what province or territory?

4. In what city, town or village have you grown up? (More than one answer is possible.)

5. What is your field of studies? 

6. How many languages do you speak? Which ones?

7. What is your first language? Or what are your first languages?

8. For how many years have you been studying French?

9. Have you lived or spent time in Quebec, France, or in another French-speaking country? If so, for how many months?

10. What French accent would you prefer to learn?
- Quebec French
- France French
- other variety of French (specify): _______________

11. Your French teacher(s) are/were mainly of what origin?
- French
- Quebec
- other (specify): ___________________


# Descriptive data and visualization

There are 44 females and 12 males
```{r gender}

data %>% select(gender) %>% 
  group_by(gender) %>%
  tally() %>% 
  mutate(prop = percent(n/sum(n)))
```

One respondent did not disclose his/her age. The ages of participants range from 18 to 39, with the mean lying in 22. 
```{r age, warning=FALSE}
data$age <-  raw_data %>% select(Q2) %>% slice(2:n())
data$age <- as.numeric(unlist(data$age))

data %>% select(age) %>%
  drop_na() %>%
  summarize(min = min(age),
            max = max(age),
            mean = mean(age))

data %>% select(age) %>%
  drop_na() %>% 
  ggplot(aes(x = age)) + 
  geom_density() + 
  geom_vline(aes(xintercept=mean(age)),
            color="blue", linetype="dashed", size=1) + 
  labs(y = 'density') + 
  annotate(x= mean(data$age, na.rm = TRUE),y=+Inf,label="Mean = 21.6",vjust=2,geom="label")

```

 Out of 56 participants, almost half of them comes from Canada (27). For the rest, a majority of participants are from Asia, which is followed by America, Europe, and Africa. 
```{r country/area of birth, warning = FALSE}
data %>% select(country_of_birth) %>%
  mutate(country_general = ifelse(country_of_birth == 'Canada', 'Canada', 'Outside of Canada'))  %>% 
  group_by(country_general) %>%
  tally()



as.data.frame(data %>% 
  select(country_of_birth) %>%
  filter(country_of_birth != 'Canada') %>%
  mutate(continent = case_when(country_of_birth %in% c('Pakistan', 'Philippines', 'China', 'Hong Kong (S.A.R.)', 'India', 'Iran', 'Japan', 'Kazakhstan', 'South Korea', 'Taiwan') ~ 'Asia',
                              country_of_birth %in% c('Brazil', 'Colombia', 'United States of America') ~ 'America',
                              country_of_birth %in% c('Croatia', 'Czech Republic', 'Russian Federation', 'United Kingdom of Great Britain and Northern Ireland') ~ 'Europe',
                              country_of_birth %in% c('Mauritius', 'Tunisia') ~ 'Africa')) %>%
  group_by(continent) %>% 
  tally()) %>%  
  ggplot(aes(x = continent, y = n, fill = continent)) + 
  geom_col() + 
  labs(y = 'count') + 
  geom_text(aes(label = n), vjust = -0.5)

```

Among 27 participants who was born in Canada, 18 of them grew up in BC. 
```{r province/territory}
data %>% 
  filter(country_of_birth == 'Canada') %>%
  select(grow_up_province) %>% 
  mutate(Grow_up_Province = ifelse(grow_up_province == "BC", 'Live in BC', 'Live outside BC')) %>%
  group_by(Grow_up_Province) %>%
  tally() 

```

Out of 56 participants, the fields of study of 13 people were/are French. One side note: 2 people have linguistics backgrounds. 
```{r Field of Study}
data %>% select(field_of_study) %>%
  mutate(french_major = ifelse(str_detect(field_of_study, "French"), TRUE, FALSE)) %>%
  group_by(french_major) %>% 
  tally()
```

Around half of participants speak three languages, which is followed by two languages, four languages, and over five languages. To be specific, all participants are at least English and French speakers
```{r Language They Speak}
language_df <- as.data.frame(data %>% 
  group_by(num_of_language) %>%
  tally())
  
language_df$num_of_language <- factor(language_df$num_of_language, levels = c("2", "3", "4", "+ de 5"))

language_df %>% 
  ggplot(aes(x= num_of_language, y= n, fill = num_of_language)) + 
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) + 
  xlab("How many languages do you speak?") 

nrow(data %>% 
  select(spoken_language) %>%
  filter(str_detect(spoken_language, 'French')))

nrow(data %>% 
  select(spoken_language) %>%
  filter(str_detect(spoken_language, 'English')))

```

```{r Mother Tongue}

language_df_II <- data %>% 
  select(mother_tongue) %>%
  mutate(English = ifelse(str_detect(mother_tongue, "English") | str_detect(mother_tongue, "Anglais"), TRUE, FALSE),
         Cantonese = ifelse(str_detect(mother_tongue,"Cantonese"), TRUE, FALSE), 
         Hindi = ifelse(str_detect(mother_tongue,"Hindi"), TRUE, FALSE),
         Mandarin = ifelse(str_detect(mother_tongue,"Mandarin"), TRUE, FALSE),      
         Korean = ifelse(str_detect(mother_tongue,"Korean"), TRUE, FALSE),
         Persian = ifelse(str_detect(mother_tongue,"Persian"), TRUE, FALSE),      
         Spanish = ifelse(str_detect(mother_tongue,"Spanish"), TRUE, FALSE),    
         Tagalog = ifelse(str_detect(mother_tongue,"Tagalog"), TRUE, FALSE))   

language_count = matrix(NA, nrow = 6, ncol = 2)

language_count[,1] <- names(language_df_II)[2:7]

for (i in 1:6){
  language_count[i,2] = as.numeric(table(language_df_II[,i+1]))[2]
}
  
language_count <- as.data.frame(language_count)
colnames(language_count) = c('mother_tongue', 'n')

# Visualization
rbind(language_count, data %>%
  select(mother_tongue_other) %>%
  drop_na() %>%
  group_by(mother_tongue_other) %>%
  tally() %>%
  rename(mother_tongue = mother_tongue_other)) %>%
  mutate(n = as.numeric(n)) %>%
  arrange(desc(n)) %>% 
  ggplot(aes(x = reorder(mother_tongue, n), y = n)) +
  geom_col() + 
  geom_text(aes(label = n), hjust = -0.5) + 
  coord_flip() + 
  labs(x = 'Mother Tongue', y = 'Count') + 
  theme_minimal()
```

```{r Years of Studying French}



# pie chart 
year_of_studying_french_df %>% 
  tally() %>% 
  ggplot(aes(x="", y = n, fill=year_group))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y") + 
  scale_fill_discrete(name = "Years of Studying French") 
  
# barchart
  
year_of_studying_french_df %>% 
  tally() %>% 
  ggplot(aes(x = year_group, y =n, fill=year_group)) +
  geom_col()+
  geom_text(aes(label = n), vjust = -0.5) + 
  labs(x = 'Years of Studying French', y = 'count')
```
10. What French accent would you prefer to learn?
- Quebec French
- France French
- other variety of French (specify): 


The number/proportion of preference for European French is over three times of that of Quebec! 
```{r Preferred French to Learn}
data %>% 
  select(type_of_french) %>% 
  mutate(type_of_french=replace(type_of_french, type_of_french== 'Français de France', 'French from France')) %>%
  group_by(type_of_french) %>%
  tally() %>% 
  slice_head(n = 3) %>%
  add_row(type_of_french = "Belgium, Franco-Ontario or Cajun", n = 2) %>%
  #mutate(type_of_french = replace(type_of_french, type_of_french == "Other variety of French (specify)", "Belgium, Franco-Ontario or Cajun")) %>%
  mutate(per =`n`/sum(`n`),
         label = paste0(n, ' (', scales::percent(per), ')')) %>% 
  ggplot(aes(x="", y = per, fill = type_of_french))+
  geom_bar(stat="identity", width = 1) +
  coord_polar("y", start=0, direction = - 1)+
  theme_void()+
  geom_text(aes(x=0.9, y = cumsum(per) - per/2, label= label)) + 
  scale_fill_discrete(name = "Preferred French to Learn") 
```


9. Have you lived or spent time in Quebec, France, or in another French-speaking country? 

```{r Lived/Spent time in French-speaking area}

# 42 people have lived in French-speaking places. 

data %>% 
  select(french_speaking_place) %>% 
  drop_na()

# translate into English
data %>% select(french_speaking_place) %>% 
  mutate(french_speaking_place_eng = case_when(french_speaking_place == "en France?"~'France',
                                               french_speaking_place =="au Québec?,en France?"~'Québec, France',
                                               french_speaking_place =="au Québec?"~'Québec',
                                               french_speaking_place =="ailleurs dans le monde francophone? Si oui, précisez où:"~'Other',
                                               french_speaking_place =="en France?,ailleurs dans le monde francophone? Si oui, précisez où:"~'France, Other',
                                               french_speaking_place =="au Québec?,en France?,ailleurs dans le monde francophone? Si oui, précisez où:" ~ 'Québec, France, Other',
                                               french_speaking_place == NA~'Never')) %>%
  group_by(french_speaking_place_eng) %>%
  tally()
 
 # 
```

```{r}
# these two "non" people never lived in French-speaking area
data %>% 
  select(french_speaking_place, french_speaking_place_other) %>%
  filter(french_speaking_place_other == 'Non')


unique(data$french_speaking_place_other)
```

10 continued: if so, for how many months?

```{r months of living in French-speaking area}
#unique(data$month_live_in_fr_env)

month_live_in_fr_env_df <- data %>% 
  select(month_live_in_fr_env) %>%
  drop_na() %>%
  mutate(month_live_in_fr_env_eng = case_when(month_live_in_fr_env == 'Moins de 1 mois'~'<1',
                                              month_live_in_fr_env == 'Entre 4 et 6 mois'~'4-6',
                                              month_live_in_fr_env == 'Entre 1 et 3 mois' ~'1-3',
                                              month_live_in_fr_env == 'Plus de 12 mois'~'>12',
                                              month_live_in_fr_env == 'Entre 7 et 12 mois'~'7-12')) %>%
  group_by(month_live_in_fr_env_eng) %>% 
  tally()


month_live_in_fr_env_df$month_live_in_fr_env_eng <- factor(month_live_in_fr_env_df$month_live_in_fr_env_eng,
                                                           levels = c("<1", "1-3", "4-6", "7-12", ">12"))

month_live_in_fr_env_df %>% ggplot(aes(x = month_live_in_fr_env_eng, y = n)) + 
  geom_col() + 
  geom_text(aes(label = n), vjust = -0.5) + 
  #coord_flip() + 
  labs(x = 'Months of Living in French-speaking Places', y = 'Month') + 
  theme_minimal()
```



```{r Teacher Origin}

teacher_origin_df <- data %>% 
  select(teacher_origin) %>% 
  mutate(teacher_origin_eng = case_when(teacher_origin == "French"~"France",
                                        teacher_origin == "Québécoise"~'Québec',
                                        teacher_origin == "Autre(s) (précisez)" ~ 'Other')) %>% 
  group_by(teacher_origin_eng) %>% 
  tally() %>%
  rename(teacher_origin = teacher_origin_eng)


teacher_original_other_df <- data %>% 
  select(teacher_origin_other) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "From everywhere, I had teachers from France, Quebec, and French Second Languages (FSL)", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "mélange + Franco-Ontarian + Haiti + many regions in Africa (Egypte/Sénégal/Côte d'Ivoire...etc)", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "French, Tanzanian, Mauritian", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Both French and Quebec.", "Both France and Québec")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Both French and Quebecois", "Both France and Québec")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "I think 3 teachers from Quebec and 2 from France.","Both France and Québec")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Both French and Quebecois, and also Anglophones", 'Multiple locations')) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "Franco-Ontarian", "Franco-ontarian")) %>% 
  mutate(teacher_origin_other = replace(teacher_origin_other, teacher_origin_other == "I don't know", NA)) %>% 
  group_by(teacher_origin_other) %>%
  tally() %>% 
  rename(teacher_origin = teacher_origin_other)


rbind(teacher_origin_df, teacher_original_other_df %>% slice_head( n = 3)) %>% 
  slice(1: 6) %>%
  mutate(n = replace(n, n == 11, 12)) %>% 
  ggplot(aes(x = reorder(teacher_origin, n), y = n)) + 
  geom_col() + 
  coord_flip() + 
  geom_text(aes(label = n), hjust = -0.5) + 
  labs(x = 'Original of French Teacher', y = 'Count')
```


```{r}
chisq.test(data$type_of_french, data$teacher_origin)

fisher.test(data$type_of_french, data$teacher_origin)
```


















