---
title: "Analysis III"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

1) Variables to look at:

- Race (last column. But many students have not answered. So I’m not sure you’ll be able to do anything with this!)

- Gender (same here, not sure you can do the stats on this, many women + too few men)

- Where they grew up (that’s a column I added)

- # of languages spoken 

- # of years of studying French

- origin of teachers  (done)

No need to look at their field of study. I didn’t translate that column.

2) The scale is the same:

1: I strongly agree

2: I agree

3: I slightly agree

4: I slightly disagree

5: I disagree

6. I strongly disagree




```{r Load Package, message=FALSE}
library(readxl)
library(ggplot2)

library(scales)
library(tidyverse)
library(tidyr)
library(tidytext)
library(reshape2)

library(ggpubr)
library(rstatix)

```


```{r}
#Les_diffe_rents_accents_du_franc_ais_November_1_2021_ENG_for_Shuyi <- read_excel("Data/Les différents accents du français - November 1 2021 - ENG for Shuyi.xlsx")

raw_data <- Les_diffe_rents_accents_du_franc_ais_November_1_2021_ENG_for_Shuyi

data <- raw_data[-1, ]

names(data)
```

```{r}
data <- data %>%
  select(-c(Q43...144, ...147, QID18_1, QID18_2, QID18_3, QID18_4,
            QID18_5, QID18_6, QID18_7, QID18_8, QID18_9, QID18_10, QID19)) %>%
  rename(gender = Q1,
         gender_other = Q1_4_TEXT, 
         age = Q2,
         country_of_birth = Q3,
         grow_up_country = ...8, 
         grow_up_province = Q41,
         grow_up_city = Q4,
         field_of_study = Q5,
         num_of_language = Q6,
         spoken_language = Q42, 
         #spoken_language_other = Q42_11_TEXT,
         mother_tongue = Q7,
         mother_tongue_other = Q7_11_TEXT,
         year_of_french = Q8,
         french_speaking_place = Q9,
         french_speaking_place_other = Q9_6_TEXT,
         month_live_in_fr_env = Q43...18,
         type_of_french = Q10,
         type_of_french_other = Q10_3_TEXT,
         teacher_origin = Q11, 
         teacher_origin_other = Q11_3_TEXT,
         race = RACE
         )
```

```{r gender prop}
data %>% 
  group_by(gender) %>%
  tally()
```


```{r race prop}
data %>% 
  group_by(race) %>% 
  tally()
```


```{r Grow-up Country}
data %>% 
  filter(str_detect(grow_up_country, 'Canada')) %>% 
  group_by(grow_up_country) %>% 
  tally()
# Out of 153 people who have answered this question, 99 people grew up in Canada, and another 9 people grew in both Canada and some other country. 


data %>% 
  drop_na(grow_up_country) %>% 
  filter(str_detect(grow_up_country, ',') |
           str_detect(grow_up_country, 'and'))%>% 
  group_by(grow_up_country) %>% 
  tally()

# 13 people grew up in more than one country 


data %>% 
  drop_na(grow_up_country) %>% 
  filter(!str_detect(grow_up_country, ',') &
         !str_detect(grow_up_country, 'and')) %>% 
  filter(grow_up_country != 'Canada') %>% 
  mutate(grow_up_continent = case_when(grow_up_country %in% c('Brunei Darussalam', 'China','Hong Kong (S.A.R.)','India','Indonesia',
                                                      'Iran','Japan','Kazakhstan','Malaysia', 'South Korea', 'Turkey',
                                                      'United Arab Emirates', 'Vietnam', 'Paskistan') ~ 'Asia',
                               grow_up_country %in% c('Czech Republic', 'Russia', 'UK', 'Ukraine') ~ 'Europe',
                               grow_up_country %in% c('Colombia','Dominica', 'United States of America', 'USA', 'Brazil') ~ 'America',
                               grow_up_country %in% c('Ethiopia','Dominica') ~ 'Africa'
                               )) %>% 
  group_by(grow_up_continent) %>% 
  tally() 

# For 140 people grew up in one country, excludind 99 who grew up in Canada, 25 ppl grew up in Asia, 10 grew up in America, 5 in Europe, amd one in Africa. 
```

```{r}
unique(data$grow_up_country)
```








































